Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-17 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
Small fixes

\begin{algorithm}[h]
\caption{\textsc{Bandit Algorithm for Strongly Linearly Separable Examples}
\label{algorithm:algorithm-for-strongly-linearly-separable-examples}}
\begin{algorithmic}[1]
{
\REQUIRE{Number of classes $K$.}
\REQUIRE{Number of rounds $T$.}
\REQUIRE{Inner product space $(V,\ip{\cdot}{\cdot})$.}
\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
\FOR{$t=1,2,\dots,T$}
\STATE{Observe feature vector $x_t \in V$}
\STATE{Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \ip{w_i^{(t)}}{x_t} \ge 0 \right\}$}
\IF{$S_t = \emptyset$}
\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
\IF{$z_t = 1$}
\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
\ELSE
\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ \\ \qquad  for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + x_t$}
\label{line:pos-update}
\ENDIF
\ELSE
\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
\IF{$z_t = 1$}
\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ \\ \qquad for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
\label{line:neg-update}
\ELSE
\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
\ENDIF
\ENDIF
\ENDFOR
}
\end{algorithmic}
\end{algorithm}

\begin{theorem}[Mistake upper bound]
\label{theorem:strongly-separable-examples-mistake-upper-bound}
Let $(V, \ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, $\gamma$ be a positive real number, $R$ be a non-negative real number. If
$L = ((x_1, y_1), (x_2, y_2), \dots, (x_T, y_T))$ is a sequence of labeled examples in
$V \times \{1,2,\dots,K\}$ such that:
\begin{enumerate}
  \item $L$ is strongly linearly separable with margin $\gamma$,
  \item for all $t$ in $\cbr{1,\ldots,T}$, $\norm{x_t} \le R$,
\end{enumerate}
then the expected number of mistakes
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
makes is at most $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$.
\end{theorem}

@@

\begin{theorem}[Mistake upper bound for kernelized algorithm]
\label{theorem:kernelized-upper-bound}
Let $k(\cdot, \cdot)$ be a positive definite kernel function and let
$\phi(\cdot)$ be the associated feature map. Let $K$ be a positive integer,
$\gamma$ be a positive real number, $R$ be a non-negative real number. If $L =
((x_1, y_1), (x_2, y_2), \dots, (x_T, y_T))$ is a sequence of labeled examples
such that:
\begin{enumerate}
  \item $((\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T))$,
  the set of examples in $L$ after feature transformation $\phi$,
  is strongly linearly separable with margin $\gamma$,
  \item for all $t$ in $\cbr{1,\ldots,T}$, $k(x_t,x_t) \le R^2$,
\end{enumerate}
then the expected number of mistakes Algorithm~\ref{algorithm:kernelized} makes
is at most $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$.
\end{theorem}

\begin{algorithm}[h]
\caption{\textsc{Kernelized Bandit Algorithm}
\label{algorithm:kernelized}}
\begin{algorithmic}[1]
{
\REQUIRE{Number of classes $K$.}
\REQUIRE{Number of rounds $T$.}
\REQUIRE{Kernel function  $k(\cdot, \cdot)$.}
\STATE{Initialize $J_1^{(1)} = J_2^{(1)} = \dots = J_K^{(1)} = \emptyset$}
\FOR{$t=1,2,\dots,T$}
\STATE{Observe feature vector $x_t$.}
\STATE{Compute \\ $S_t = \left\{ i ~:~ 1 \le i \le K, \ \sum_{(x,y) \in J_i^{(t)}} y k(x, x_t) \ge 0 \right\}$}
\IF{$S_t = \emptyset$}
\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
\IF{$z_t = 1$}
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
\ELSE
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ \\ \qquad  for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\STATE{Update $J_{\widehat y_t}^{(t+1)} = J_{\widehat y_t}^{(t)} \cup \cbr{(x_t, +1)}$}
\ENDIF
\ELSE
\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
\IF{$z_t = 1$}
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ \\ \qquad for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\STATE{Update $J_{\widehat y_t}^{(t+1)} = J_{\widehat y_t}^{(t)} \cup \cbr{(x_t, -1)}$}
\ELSE
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
\ENDIF
\ENDIF
\ENDFOR
}
\end{algorithmic}
\end{algorithm}

>>>>

\begin{algorithm}[h]
\caption{\textsc{Bandit Algorithm for Strongly Linearly Separable Examples}
\label{algorithm:algorithm-for-strongly-linearly-separable-examples}}
\begin{algorithmic}[1]
{
\REQUIRE{Number of classes $K$, number of rounds $T$.}
\REQUIRE{Inner product space $(V,\ip{\cdot}{\cdot})$.}
\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
\FOR{$t=1,2,\dots,T$}
\STATE{Observe feature vector $x_t \in V$}
\STATE{Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \ip{w_i^{(t)}}{x_t} \ge 0 \right\}$}
\IF{$S_t = \emptyset$}
\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
\IF{$z_t = 1$}
\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
\ELSE
\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ \\ \qquad  for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + x_t$}
\label{line:pos-update}
\ENDIF
\ELSE
\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
\IF{$z_t = 1$}
\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ \\ \qquad for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
\label{line:neg-update}
\ELSE
\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
\ENDIF
\ENDIF
\ENDFOR
}
\end{algorithmic}
\end{algorithm}

\begin{theorem}[Mistake upper bound]
\label{theorem:strongly-separable-examples-mistake-upper-bound}
Let $(V, \ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, $\gamma$ be a positive real number, $R$ be a non-negative real number.
If the examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in V \times
\{1,2,\dots,K\}$ are strongly linearly separable with margin $\gamma$ and for
all $t \in \cbr{1,\ldots,T}$ satisfy $\norm{x_t} \le R$ then the expected number
of mistakes
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
makes is at most $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$.
\end{theorem}

@@

\begin{theorem}[Mistake upper bound for kernelized algorithm]
\label{theorem:kernelized-upper-bound}
Let $X$ be a non-empty set, let $(V, \ip{\cdot}{\cdot})$ be an inner product
space. Let $\phi:X \to V$ be a feature map and let $k:X \times X \to \R$,
$k(x,x') = \ip{\phi(x)}{\phi(x')}$ the associated positive positive definite
kernel. Let $K$ be a positive integer, $\gamma$ be a positive real number, $R$
be a non-negative real number. If $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in
X \times \{1,2,\dots,K\}$ are labeled examples such that:
\begin{enumerate}
\item the mapped examples $(\phi(x_1), y_1)$, $(\phi(x_2), y_2)$, $\dots$, $(\phi(x_T), y_T)$
are strongly linearly separable with margin $\gamma$,
\item for all $t$ in $\cbr{1,\ldots,T}$, $k(x_t,x_t) \le R^2$,
\end{enumerate}
then the expected number of mistakes Algorithm~\ref{algorithm:kernelized} makes
is at most $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$.
\end{theorem}

\begin{algorithm}[h]
\caption{\textsc{Kernelized Bandit Algorithm}
\label{algorithm:kernelized}}
\begin{algorithmic}[1]
{
\REQUIRE{Number of classes $K$, number of rounds $T$.}
\REQUIRE{Kernel function  $k(\cdot, \cdot)$.}
\STATE{Initialize $J_1^{(1)} = J_2^{(1)} = \dots = J_K^{(1)} = \emptyset$}
\FOR{$t=1,2,\dots,T$}
\STATE{Observe feature vector $x_t$.}
\STATE{Compute \\ $S_t = \left\{ i ~:~ 1 \le i \le K, \ \sum_{(x,y) \in J_i^{(t)}} y k(x, x_t) \ge 0 \right\}$}
\IF{$S_t = \emptyset$}
\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
\IF{$z_t = 1$}
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
\ELSE
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ \\ \qquad  for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\STATE{Update $J_{\widehat y_t}^{(t+1)} = J_{\widehat y_t}^{(t)} \cup \cbr{(x_t, +1)}$}
\ENDIF
\ELSE
\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
\IF{$z_t = 1$}
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ \\ \qquad for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\STATE{Update $J_{\widehat y_t}^{(t+1)} = J_{\widehat y_t}^{(t)} \cup \cbr{(x_t, -1)}$}
\ELSE
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
\ENDIF
\ENDIF
\ENDFOR
}
\end{algorithmic}
\end{algorithm}

### 2019-01-17 ICML-submission/from-weak-separability-to-strong-separability.tex
Small fixes

In this section, we consider case when the examples are weakly linearly
separable. Throughout this section, we assume without loss of generality that
all examples lie in the unit ball $\B(0,1) \subseteq \R^d$.\footnote{Instead of
working with feature vector $x_t$ we can work with normalized feature vectors
$\widehat{x}_t = \frac{x_t}{\norm{x_t}}$. It can be easily checked that if
$(x_1,y_1), (x_2,y_2), \dots, (x_T,y_T)$ are weakly linearly separable with
margin $\gamma$ and $\norm{x_t} \le R$ for all $t$, then the normalized examples
$(\widehat{x}_1,y_1), (\widehat{x}_2,y_2), \dots, (\widehat{x}_T,y_T)$ are weakly
linearly separable by margin $\gamma/R$.} Note that
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
alone does not guarantee a finite mistake bound in this setting, as weak linear
separability does not imply strong linear separability.

>>>>

In this section, we consider case when the examples are weakly linearly
separable. Throughout this section, we assume without loss of generality that
all examples lie in the unit ball $\B(0,1) \subseteq \R^d$.\footnote{Instead of
working with feature vector $x_t$ we can work with normalized feature vectors
$\widehat{x}_t = \frac{x_t}{\norm{x_t}}$. It can be easily checked that if
$(x_1,y_1), (x_2,y_2), \dots, (x_T,y_T)$ are weakly linearly separable with
margin $\gamma$ and $\norm{x_t} \le R$ for all $t$, then the normalized examples
$(\widehat{x}_1,y_1), (\widehat{x}_2,y_2), \dots, (\widehat{x}_T,y_T)$ are weakly
linearly separable with margin $\gamma/R$.} Note that
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
alone does not guarantee a finite mistake bound in this setting, as weak linear
separability does not imply strong linear separability.

### 2019-01-17 ICML-submission/notions-of-linear-separability.tex
Small fixes

\begin{definition}[Weak linear separability]
\label{definition:weak-linear-separability}
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. Let $L = ((x_1, y_1), (x_2,
y_2), \dots, (x_T, y_T))$ be a sequence of labeled examples in $V \times
\{1,2,\dots,K\}$.

$L$ is said to be \emph{weakly linearly separable with a margin $\gamma$} if
there exist vectors $w_1, w_2, \dots, w_K \in V$ such that
\begin{align}
\label{equation:weak-linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:weak-linear-separability-2}
& \begin{gathered}
\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
\ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; .
\end{gathered}
\end{align}
\end{definition}

\begin{definition}[Strong linear separability]
\label{definition:strong-linear-separability}
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. Let $L = ((x_1, y_1), (x_2,
y_2), \dots, (x_T, y_T))$ be a sequence of labeled examples in $V \times
\{1,2,\dots,K\}$.

$L$ is said to be \emph{strongly linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:strong-linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:strong-linear-separability-2}
& \forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \frac \gamma 2 \; , \\
\label{equation:strong-linear-separability-3}
& \begin{gathered}
\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
\ip{x_t}{w_i} \le - \frac \gamma 2 \; .
\end{gathered}
\end{align}
\end{definition}

The notion of weak linear separability with a margin is standard. It is used in
the full-information setting to upper bound the number of mistakes of the
\textsc{Multiclass Perceptron} algorithm. It is a folklore result that if a set
of labeled examples is separable with a margin $\gamma$ and the norm of the
examples is bounded by $R$, then \textsc{Multiclass Perceptron} algorithm makes
at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$ mistakes. Another folklore
result is that \textsc{Multiclass Perceptron} is essentially optimal in the
sense that any (possibly randomized) algorithm must make $\frac{1}{2}
\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. For
completeness, we state the \textsc{Multiclass Perceptron} algorithm and give
proofs of both of these results in
Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
material.

\chicheng{Shall we mention that this multiclass margin notion has also appeared in e.g.~\cite{Crammer-Singer-2003}?}

@@

It is easy to see that if a sequence of labeled examples is strongly linearly
separable with margin $\gamma$, then it is also weakly linearly separable with
the same margin. Indeed, if $w_1, w_2, \dots, w_K \in V$ satisfy
\eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2},
\eqref{equation:strong-linear-separability-3} then they satisfy
\eqref{equation:weak-linear-separability-1} and
\eqref{equation:weak-linear-separability-2}.

In the special case of $K=2$, if a sequence of labeled examples is weakly
linearly separable with a margin $\gamma$, then it is also strongly linearly
separable with the same margin. Indeed, if $w_1, w_2$ satisfy
\eqref{equation:weak-linear-separability-1} and
\eqref{equation:weak-linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$,
$w_2' = \frac{w_2 - w_1}{2}$ satisfy
\eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2},
\eqref{equation:strong-linear-separability-3}.
Equation~\eqref{equation:strong-linear-separability-1} follows from
$\norm{w_i'}^2 \le (\frac{1}{2} \norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le
\frac{1}{2}\norm{w_1}^2 + \frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$.
Equations~\eqref{equation:strong-linear-separability-2}
and~\eqref{equation:strong-linear-separability-3} follow from the fact that
$w_1' - w_2' = w_1 - w_2$.

@@

\begin{figure}
\begin{center}
\input{figures/weakly-linearly-separable-examples-with-margin}
\end{center}
\caption[]{A set of labeled examples in $\R^2$. The examples belong to
$K=3$ classes colored white, gray and black respectively. Each class lies in a
$120^\circ$ wedge. In other words, each class lies in an intersection of two
halfspaces.
\chicheng{Do we have an explicit formula for $W$ in this example? It might help
to provide it.}

While the examples are weakly linearly separable with a positive margin
$\gamma$, they are \emph{not} strongly linearly separable with any positive
margin $\gamma$. For instance, there does \emph{not} exist a linear separator
that separates the examples belonging to the gray class from the examples
belonging to the remaining two classes.
}
\label{figure:weakly-linearly-separable-examples-with-margin}
\end{figure}

>>>>

\begin{definition}[Weak linear separability]
\label{definition:weak-linear-separability}
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. Labeled examples $(x_1, y_1),
(x_2, y_2), \dots, (x_T, y_T) \in V \times \{1,2,\dots,K\}$ are said to be
\emph{weakly linearly separable with a margin $\gamma$} if there exist vectors
$w_1, w_2, \dots, w_K \in V$ such that
\begin{align}
\label{equation:weak-linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:weak-linear-separability-2}
& \begin{gathered}
\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
\ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; .
\end{gathered}
\end{align}
\end{definition}

\begin{definition}[Strong linear separability]
\label{definition:strong-linear-separability}
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. Labeled examples $(x_1, y_1),
(x_2, y_2), \dots, (x_T, y_T) \in V \times \{1,2,\dots,K\}$ are said to be
\emph{strongly linearly separable with a margin $\gamma$} if there exist vectors
$w_1, w_2, \dots, w_K \in V$ such that
\begin{align}
\label{equation:strong-linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:strong-linear-separability-2}
& \forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \frac \gamma 2 \; , \\
\label{equation:strong-linear-separability-3}
& \begin{gathered}
\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
\ip{x_t}{w_i} \le - \frac \gamma 2 \; .
\end{gathered}
\end{align}
\end{definition}

The notion of weak linear separability is a standard assumption used in the
full-information setting to upper bound the number of mistakes of the
\textsc{Multiclass Perceptron} algorithm. Namely, \citet{Crammer-Singer-2003}
prove that if the examples are weakly linearly separable with a margin $\gamma$
and the norm of the examples is bounded by $R$, then \textsc{Multiclass
Perceptron} algorithm makes at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
mistakes. It is a folklore result that \textsc{Multiclass Perceptron} is
essentially optimal in the sense that any (possibly randomized) algorithm must
make $\frac{1}{2} \left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the
worst case. For completeness, we state the \textsc{Multiclass Perceptron}
algorithm and give proofs of both of these results in
Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
material.

@@

It is easy to see that if a set of labeled examples is strongly linearly
separable with margin $\gamma$, then it is also weakly linearly separable with
the same margin. Indeed, if $w_1, w_2, \dots, w_K \in V$ satisfy
\eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2},
\eqref{equation:strong-linear-separability-3} then they satisfy
\eqref{equation:weak-linear-separability-1} and
\eqref{equation:weak-linear-separability-2}.

In the special case of $K=2$, if a set of labeled examples is weakly
linearly separable with a margin $\gamma$, then it is also strongly linearly
separable with the same margin. Indeed, if $w_1, w_2$ satisfy
\eqref{equation:weak-linear-separability-1} and
\eqref{equation:weak-linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$,
$w_2' = \frac{w_2 - w_1}{2}$ satisfy
\eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2},
\eqref{equation:strong-linear-separability-3}.
Equation~\eqref{equation:strong-linear-separability-1} follows from
$\norm{w_i'}^2 \le (\frac{1}{2} \norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le
\frac{1}{2}\norm{w_1}^2 + \frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$.
Equations~\eqref{equation:strong-linear-separability-2}
and~\eqref{equation:strong-linear-separability-3} follow from the fact that
$w_1' - w_2' = w_1 - w_2$.

@@

\begin{figure}
\begin{center}
\input{figures/weakly-linearly-separable-examples-with-margin}
\end{center}
\caption[]{A set of labeled examples in $\R^2$. The examples belong to
$K=3$ classes colored white, gray and black respectively. Each class lies in a
$120^\circ$ wedge. In other words, each class lies in an intersection of two
halfspaces. While the examples are weakly linearly separable with a positive margin
$\gamma$, they are \emph{not} strongly linearly separable with any positive
margin $\gamma$. For instance, there does \emph{not} exist a linear separator
that separates the examples belonging to the gray class from the examples
belonging to the remaining two classes.
}
\label{figure:weakly-linearly-separable-examples-with-margin}
\end{figure}
